Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review

### 2021-03-23 Article.Rmd
Bookdown

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
output: 
  bookdown::word_document2:
    reference_docx: "article_template.docx"
bibliography: library.bib
csl: bmj.csl

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

>>>>

---
title: "Mapping the current knowledge in syndemic research applied to Men who have Sex with Men : a Scoping Review"
author: 
- "Maxence R. Ouafik^1^, Laetitia Buret^2^, Jean-Luc Belche^3^, Beatrice Scholtes^4^"
- "^1^ Corresponding author at : General Practice Department - Primary Care and Health Research Unit, MD - PhD student,  University of Liège, Liège, Belgium <maxence.ouafik@uliege.be> ; Quartier Hôpital B23 Avenue Hippocrate 13 4000 Liège ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0002-9795-5721"
- "^2^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, research assistant, University of Liège, Liège, Belgium <laetitia.buret@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-6039-9824"
- "^3^ General Practice Department - Primary Care and Health Research Unit, MD - GP - PhD, lecturer, University of Liège, Liège, Belgium <jlbelche@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-8807-0473"
- "^4^ General Practice Department - Primary Care and Health Research Unit, Postdoctoral Researcher,  University of Liège, Liège, Belgium <beatrice.scholtes@uliege.be> ![OrcID](./Files/Images/OrcID.png) https://orcid.org/0000-0001-5274-822X"
output: 
  bookdown::word_document2:
    reference_docx: "article_template.docx"
csl: bmj.csl
bibliography: references.bib
link-citations: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(bookdown)
```

# Results

## Literature search

You can find the complete flowchart in Figure \@ref(fig:PRISMA)

```{r PRISMA, fig.cap = "PRISMA flowchart of the included search strategy"}
knitr::include_graphics("Files/images/PRISMA.png")

```

## How are studies concerning Syndemic Theory applied to MSM conducted?

### General characteristics of included studies

### Subpopulations studied

### Syndemic conditions and their measurement

### Outcomes and their measurement

### Interventions

## How is the concept of interaction explored in syndemic research applied to MSM?

### Statistics used to show an interaction

### Proposed mechanisms of interaction

## What were the key findings of these studies?

# Discussion

# Conclusion
